Models of gravitational lens candidates from Space Warps CFHTLS

### 2017-08-24 parts/stelmass.tex
some changes
elaborate M_stell error range in fig6

\section{Stellar and halo mass estimates}\label{sec:stellar-mass}

@@

Figure~\ref{fig:stelmass} shows a comparison of stellar and total
masses.  The comparatively large uncertainty in the stellar mass will
be improved in future work by using available optical and NIR
magnitudes to derive more accurate constraints on the stellar
populations.

>>>>

\section{Stellar and halo mass estimates}
\label{sec:stellar-mass}

@@

Figure~\ref{fig:stelmass} shows a comparison of stellar and total
masses.  The comparatively large span in the stellar mass shows the range 
between the masses derived using the two age trends respectively.
It will 
be improved in future work by using available optical and NIR
magnitudes to derive more accurate constraints on the stellar
populations.
